What We Eval in the Shadows

### 2021-04-16 paper/main.tex
SE discussion

\begin{table}[h]
  \small
  \centering
  \begin{tabular}{l|r|r|r|r}\hline
    Environments & \#sites & \%sites & \#funs. & \%funs. \\%
    \expandableinput tag/table-se-target-envs.tex
  \end{tabular}
  \caption{Most used target environments for \eval side-effects} \label{tab:se-env}
\end{table}

@@

\mypara{Discussion}
\todo{Is there any comparison with JS?}

>>>>

\begin{wraptable}{r}{7cm}\small\centering
  \small
  \centering
  \begin{tabular}{l|r|r|r|r}\hline
    Environments & \#sites & \%sites & \#funs. & \%funs. \\%
    \expandableinput tag/table-se-target-envs.tex
  \end{tabular}
  \caption{Target environments for \eval side-effects} \label{tab:se-env}
\end{wraptable}

@@

\mypara{Discussion} In JavaScript assignments in \eval can happen in either
local scope or less often, when called through an alias, in the global scope.
In R, given the support for first-class environments, it can happen anywhere.
The data however suggest that most of side effects from \eval happen in a
predictable environment.
